### 2020-07-10 article.tex
Add myself as a co-author
Add xSDK reference

% Optional PDF information
\ifpdf
\hypersetup{
  pdftitle={KSPHPDDM and PCHPDDM: Extending PETSc with Robust Overlapping Schwarz Preconditioners and Advanced Krylov Methods},
  pdfauthor={P. Jolivet and S. Zampini}
}
\fi

@@

\section{Introduction}
Implementing and maintaining robust and scalable applications is highly relevant
in the field of computational science and engineering. The efficient production of
such applications requires a rich ecosystem of state-of-the-art reusable libraries
\cite{xsdk}. In this paper, we focus on the interoperability of two such libraries.

@@

\section*{Acknowledgments}
The authors would like to thank S. Balay, J. Brown, V. Hapla, M. Knepley, J.
Roman, and B. Smith for reviewing the successive merge requests in PETSc and
SLEPc repositories. This work was granted access to the GENCI-sponsored HPC resources of:
\begin{itemize}
    \item TGCC@CEA under allocation A0070607519;
    \item IDRIS@CNRS under allocation AP010611780.
\end{itemize}
% We would like to acknowledge the assistance of volunteers in putting
% together this example manuscript and supplement.

@@

>>>>

% Optional PDF information
\ifpdf
\hypersetup{
  pdftitle={KSPHPDDM and PCHPDDM: Extending PETSc with Robust Overlapping Schwarz Preconditioners and Advanced Krylov Methods},
  pdfauthor={P. Jolivet, J. E. Roman, and S. Zampini}
}
\fi

@@

\section{Introduction}
Implementing and maintaining robust and scalable applications is highly relevant
in the field of computational science and engineering. The efficient production of
such applications requires a rich ecosystem of state-of-the-art reusable libraries
\cite{Bartlett:2017:XFT}. In this paper, we focus on the interoperability of two such libraries.

@@

\section*{Acknowledgments}
The authors would like to thank S. Balay, J. Brown, V. Hapla, M. Knepley,
and B. Smith for reviewing the successive merge requests in the PETSc
repository. This work was granted access to the GENCI-sponsored HPC resources of:
\begin{itemize}
    \item TGCC@CEA under allocation A0070607519;
    \item IDRIS@CNRS under allocation AP010611780.
\end{itemize}
% We would like to acknowledge the assistance of volunteers in putting
% together this example manuscript and supplement.

@@

\bibitem{Bartlett:2017:XFT}
{\sc R.~Bartlett, I.~Demeshko, T.~Gamblin, G.~Hammond, M.~A. Heroux,
  J.~Johnson, A.~Klinvex, X.~Li, L.~C. McInnes, J.~D. Moulton, D.~Osei-Kuffuor,
  J.~Sarich, B.~Smith, J.~Willenbring, and U.~M. Yang}, {\em {xSDK}
  foundations: Toward an extreme-scale scientific software development kit},
  Supercomputing Frontiers and Innovations, 4 (2017),
  \url{https://doi.org/10.14529/jsfi170104}.
